\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{enumitem}

\title{\textbf{KritiAI: Multimodal Document Intelligence and Cross-Modal Action Brain for Regional Governance}}
\author{Vedic Dutta \and Shaswata K Banik}
\date{IIT Kharagpur Platinum Jubilee Innovation Challenge\\Track A: Deep Tech for the World}

\begin{document}

\maketitle

\begin{abstract}
Regional administrative offices in India operate in fragmented, paper-heavy, and bilingual ecosystems. Public employees waste millions of man-hours manually drafting, verifying, and auditing files, particularly in agricultural workflows such as disaster compensation claims. Standard enterprise AI solutions fail because they cannot process unstructured, localized paper records or ground them against physical reality. KritiAI addresses this gap by constructing a unified Cross-Modal Regional Intelligence Engine. By utilizing lightweight adapter technologies on top of existing foundation models, KritiAI mathematically aligns unstructured administrative claims (processed via Vision-Language Models) with physical Earth-surface realities (via multi-year spatial-temporal embeddings like AlphaEarth). This report outlines our v0 MVP architecture, demonstrating real-time, deterministic auditing of PMFBY crop-failure claims.
\end{abstract}

\section{Introduction}
When a farmer applies for disaster compensation (e.g., via the PMFBY scheme) after a thunderstorm, the verification process requires cross-referencing messy historical paper archives with physical terrain realities. This manual auditing process takes 3 to 6 months, leading to severe bureaucratic backlogs and vulnerability to documentation fraud. KritiAI acts as the definitive organizational brain to automate this workflow by transforming dead paper records into an actionable intelligence layer.

\section{System Architecture}
Our core technical innovation lies in Cross-Modal Grounding—aligning low-resource text against spatio-temporal environments. The v0 prototype consists of three primary layers.

\subsection{Data Ingestion \& VLM Pipeline (The Parsing Layer)}
To process chaotic paper trails, the engine uses layout-aware Vision-Language Models (VLMs) like Gemini 2.5 Flash. The model simultaneously reads handwritten text and analyzes its spatial layout, extracting structured data (Farmer Name, Khasra Number, Claimed Disaster) while preserving critical structural context such as official department seals.

\subsection{Environmental Context (The Grounding Layer)}
To ground the claim in physical reality without expensive infrastructure, the engine ingests pre-computed, self-supervised environmental and atmospheric embedding models. Specifically, we simulate the integration of AlphaEarth foundational tensors—64-dimensional feature vectors per 10m pixel representing land-surface dynamics from optical and radar data. 

\subsection{Cross-Modal Alignment (The Brain)}
A Retrieval-Augmented Generation (RAG) pipeline combined with a Hierarchical Reasoning Model (HRM) logic block forms the core engine. We calculate a mathematical anomaly score by taking the cosine distance between the farm's current 64D AlphaEarth vector and a healthy baseline. The LLM evaluates how the written administrative claim aligns with this physical history, outputting a deterministic Audit Decision (VERIFIABLE or DISCREPANCY FOUND).

\section{Future Roadmap}
\begin{itemize}
    \item \textbf{Intelligent Onboarding Engine:} A guided workflow to automatically pre-process context and prepare tailored investigation questions for office workers.
    \item \textbf{Deep Vector Integration:} Live API connections to Google Earth Engine for real-time 64D spatial-temporal embedding extraction across multiple years.
    \item \textbf{Short Audits via Firehoses:} Integration of live unstructured data streams (e.g., X, local news reports) to run immediate short audits correlating claimed disaster dates with localized social chatter.
\end{itemize}

\section{Conclusion}
KritiAI proves that deep tech can be localized and parameter-efficient. By projecting different modalities into a single vector space for mathematical alignment, we achieve near-zero-hallucination processing, fundamentally solving the administrative paralysis of regional governance.

\end{document}
